Analyses

### 2023-11-07 analyses.Rmd
- integrated reviewer feedback

    # fit model
    fit <- 
      hush(
        brm(
          bf(
            formula_mdl, 
            formula_hrdl
            ), 
          data = object, 
          family = hurdle_gamma(),
          silent = TRUE,
          refresh = 0
          )
      )

@@

# variable labels
var_names <- c(
  "Privacy concerns", 
  "General gratifications", 
  "Specific gratifications",
  "Privacy deliberation", 
  "Self-efficacy", 
  "General trust", 
  "Specific trust",
  "Words log"
  )

var_names_breaks <- c(
  "Privacy\nconcerns", 
  "General\ngratifications", 
  "Specific\ngratifications",
  "Privacy\ndeliberation", 
  "Self-\nefficacy", 
  "General\ntrust", 
  "Specific\ntrust",
  "Words (log)"
  )

@@

```{r}
run_hurdles(
  object = d,
  name = "wrds_ctrl",
  outcome = "words", 
  predictor = "version",
  y_lab = "Words",
  x_lab = "Experimental conditions"
  )
```

@@

```{r}
run_hurdles(
  object = d, 
  name = "wrds_lkdslk",
  outcome = "words", 
  predictor = "version_lkdslk",
  y_lab = "Words",
  x_lab = "Experimental conditions"
  )
```

@@

```{r}
run_hurdles(
  object = d,
  name = "pricon_ctrl",
  outcome = "pri_con_fs", 
  predictor = "version",
  y_lab = "Privacy concerns",
  x_lab = "Experimental conditions"
  )
```

@@

#### Expected Gratifications

@@

```{r}
run_hurdles(
  object = d,
  name = "grats_ctrl",
  outcome = "grats_gen_fs", 
  predictor = "version",
  y_lab = "Gratifications",
  x_lab = "Experimental conditions"
  )
```

@@

#### Trust

@@

```{r}
run_hurdles(
  object = d,
  name = "trust_ctrl",
  outcome = "trust_gen_fs", 
  predictor = "version",
  y_lab = "Trust",
  x_lab = "Experimental conditions"
  )
```

@@

```{r}
run_hurdles(
  object = d, 
  name = "trust_lkdslk",
  outcome = "trust_gen_fs", 
  predictor = "version_lkdslk",
  y_lab = "Trust",
  x_lab = "Experimental conditions"
  )
```

@@

#### Expected Gratifications

```{r}
run_hurdles(
  object = d, 
  name = "wrds_grats",
  outcome = "words", 
  predictor = "grats_gen_fs",
  y_lab = "Words",
  x_lab = "Expected gratifications"
  )
```

@@

#### Trust

```{r}
run_hurdles(
  object = d, 
  name = "wrds_trust",
  outcome = "words", 
  predictor = "trust_gen_fs",
  y_lab = "Words",
  x_lab = "Trust"
  )
```

@@

```{r}
run_hurdles(
  object = d, 
  name = "wrds_selfeff",
  outcome = "words", 
  predictor = "self_eff_fs",
  y_lab = "Words",
  x_lab = "Self-Efficacy"
  )
```

@@

ggsave("figures/results/effects.pdf")
ggsave("figures/results/effects.png")
```

>>>>

    # fit model
    fit <- 
      hush(
        brm(
          bf(
            formula_mdl, 
            formula_hrdl
            ), 
          data = object, 
          family = hurdle_gamma(),
          silent = TRUE,
          refresh = 0,
          iter = 1000,
          backend = "cmdstanr"
          )
      )

@@

# variable labels
var_names <- c(
  "Privacy concerns", 
  "Gratifications general", 
  "Gratifications specific",
  "Privacy deliberation", 
  "Self-efficacy", 
  "Trust general", 
  "Trust specific",
  "Words log"
  )

var_names_breaks <- c(
  "Privacy\nconcerns", 
  "Gratifications\ngeneral", 
  "Gratifications\nspecific",
  "Privacy\ndeliberation", 
  "Self-\nefficacy", 
  "Trust\ngeneral", 
  "Trust\nspecific",
  "Words (log)"
  )

@@

```{r words}
run_hurdles(
  object = d,
  name = "wrds_ctrl",
  outcome = "words", 
  predictor = "version",
  y_lab = "Words",
  x_lab = "Experimental conditions"
  )
```

@@

```{r words-lkdslk}
run_hurdles(
  object = d, 
  name = "wrds_lkdslk",
  outcome = "words", 
  predictor = "version_lkdslk",
  y_lab = "Words",
  x_lab = "Experimental conditions"
  )
```

@@

```{r pricon-ctrl}
run_hurdles(
  object = d,
  name = "pricon_ctrl",
  outcome = "pri_con_fs", 
  predictor = "version",
  y_lab = "Privacy concerns",
  x_lab = "Experimental conditions"
  )
```

@@

#### Gratifications General

@@

```{r}
run_hurdles(
  object = d,
  name = "grats_ctrl",
  outcome = "grats_gen_fs", 
  predictor = "version",
  y_lab = "Gratifications general",
  x_lab = "Experimental conditions"
  )
```

@@

#### Trust general

@@

```{r}
run_hurdles(
  object = d,
  name = "trust_ctrl",
  outcome = "trust_gen_fs", 
  predictor = "version",
  y_lab = "Trust general",
  x_lab = "Experimental conditions"
  )
```

@@

```{r}
run_hurdles(
  object = d, 
  name = "trust_lkdslk",
  outcome = "trust_gen_fs", 
  predictor = "version_lkdslk",
  y_lab = "Trust general",
  x_lab = "Experimental conditions"
  )
```

@@

#### Gratifications General

```{r}
run_hurdles(
  object = d, 
  name = "wrds_grats",
  outcome = "words", 
  predictor = "grats_gen_fs",
  y_lab = "Words",
  x_lab = "Gratifications general"
  )
```

@@

#### Trust General

```{r}
run_hurdles(
  object = d, 
  name = "wrds_trust",
  outcome = "words", 
  predictor = "trust_gen_fs",
  y_lab = "Words",
  x_lab = "Trust general"
  )
```

@@

```{r}
run_hurdles(
  object = d, 
  name = "wrds_selfeff",
  outcome = "words", 
  predictor = "self_eff_fs",
  y_lab = "Words",
  x_lab = "Self-efficacy"
  )
```

@@

# Save visualizations
ggsave("figures/results/effects.pdf")
ggsave("figures/results/effects.png")
```
